Analysis of pudding following Davidson 1970

### 2021-11-04 inst/pudding.Rmd
more work

# Appendix: a synthetic dataset

@@

(above we see that pudding 1 does indeed have a highing tie
probability).  Test the null of equal tying probabilities:

@@

>>>>

# Appendix:  synthetic datasets

@@

(above we see that pudding 1 does indeed have a higher tie
probability).  Test the null of equal tying probabilities:

@@

## Test of Davidson vs Hankin

Although the likelihood for Davidson's model was higher than mine for
the original dataset, we can create a synthetic dataset which is a
random observation drawn from a reified Bradley-Terry probability
model.  I will then test the hypothesis that the data is in fact drawn
from an RBT distribution by calculating a likelihood ratio.

```{r,synthmaker}
set.seed(2)
f <- function(i){rmultinom(1,50,prob=h[i,])} # f(i) = sample from row i of h
synth <- pudding_table
synth[,-(1:3)] <- t(sapply(1:15,f))  # random sample
synth[,3] <- 50
rownames(synth) <- rownames(p)
colnames(synth) <- colnames(p)
synth
```

Above, `synth` is a dataset drawn from an RBT model with maximum
likelihood parameters obtained from the original dataset.  We now use
both methods.  First reified Bradley-Terry:

```{r,useboth,cache=TRUE}
(H_synth <- convert(synth)[[1]])
ph_synth <- maxp(H_synth)
```

```{r}
ph_synth
```

The above strengths are different from (but not too different from)
the value obtaine from `maxp(H)` above.  Now analyse the same dataset
but using the method given in the `PlackettLuce` vignette:

```{r}
PlackettLuce_coef <- function(pudding_table){
i_wins <- data.frame(Winner = pudding_table$i, Loser = pudding_table$j)
j_wins <- data.frame(Winner = pudding_table$j, Loser = pudding_table$i)
  ties <- data.frame(Winner = asplit(pudding_table[c("i", "j")], 1),
                     Loser = rep(NA, 15))
R <- as.rankings(rbind(i_wins, j_wins, ties),
                 input = "orderings")
w <- unlist(pudding_table[c("w_ij", "w_ji", "t_ij")])
mod <- PlackettLuce(R, weights = w, npseudo = 0, maxit = 7)
return(coef(mod,log=FALSE))
}	
```

As a consistency check, try verifying the original result:

```{r,verifypl,cache=TRUE}
PlackettLuce_coef(pudding_table)
```

Above, we see values that match those in the `PlackettLuce` vignette.
Now apply the same method to the synthetic dataset `synth`:

```{r,calcpdsynth,cache=TRUE}
(pd_synth <- PlackettLuce_coef(synth))
```

Now we need to calculate the probabilities:

```{r}
(h_synth <- hankin(ph_synth))
(d_synth <- davidson(pd_synth))
```

And calculate a likelihood ratio for the two hypotheses, RBT and
Davidson:

```{r}
(n <- synth[,-(1:3),])
(lh_synth <- sum(n*log(h_synth)))
(ld_synth <- sum(n*log(d_synth)))
lh_synth - ld_synth
```

So reified Bradley-Terry is better than Davidson, but (in this case at
least) not by much.
